CS222 Project Proposal

### 2019-12-10 proposal/proposal.tex

>>>>

% ensemble
A similar method that uses several weak learners to accomplish tasks is the ensemble method, which has been explored by many researchers. 
Beriman\cite{BreimanBagging} proposed a method for generating multiple versions of a predictor by making bootstrap replicates of the learning set. 
However, this method actually increased the amount of computation since it trained the learned repeatedly.
Schapire\cite{Schapire1989The} proposed the boosting method to converting a weak learning algorithm into one that achieved arbitrarily high accuracy by combining a set of weak learners.
This method was developed by Freund \textit{et al.}\cite{Freund1995A}, who proposed an adaptive version of the boost.
Subsequent weak learners were tweaked in favor of those instances misclassified by previous classifiers. 
Friedman \textit{et al.}\cite{FriedmanGreedy} proposed a new method called gradient boosting. 
It performed additive optimization in functional space, which compensated for the weakness of weak classifiers in the light of the gradient of their loss function.
